---
title: "COVID-19 in the Greater Region"
output: 
  flexdashboard::flex_dashboard:
    source_code: embed
---

```{r global, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

tar_load(raw_weekly_data)
tar_load(raw_weekly_long)

raw_weekly_data_shared <- SharedData$new(raw_weekly_data)
raw_weekly_long_shared <- SharedData$new(raw_weekly_long)
```

Weekly COVID-19 cases and deaths detected by country (table) {data-navmenu="Choose tab"}
======================================================================================================

Inputs {.sidebar}
-------------------------------------------------------------------------

```{r}
filter_checkbox("country", "Choose country", raw_weekly_data_shared, ~country)
filter_select("year_month", "Choose month of the year", raw_weekly_data_shared, ~year_month)
filter_slider("week_date", "Filter cases", raw_weekly_data_shared, ~cases, width = "100%")
```

Column
-------------------------------------------------------------------------


### Weekly positive cases and deaths
 
```{r}

datatable(raw_weekly_data_shared,
          class = "compact cell-border",
          rownames = FALSE,
          options = list(order = list(1, "desc"),
                         autoWidth = FALSE,
                         pageLength = 20))
```
    
    
Weekly COVID-19 cases and deaths detected by country (Pivot Table) {data-navmenu="Choose tab"}
======================================================================================================


Column
-------------------------------------------------------------------------


### Weekly positive cases and deaths
   
```{r}
tar_read(raw_weekly_data) %>%
  rpivotTable()
```


Weekly COVID-19 cases and deaths detected by country (animated map) {data-navmenu="Choose tab"}
======================================================================================================


Column
-------------------------------------------------------------------------


### Weekly positive cases and deaths
 
```{r}
tar_read(interactive_plot)
```


Weekly COVID-19 cases and deaths detected by country (epidemic curves) {data-navmenu="Choose tab"}
======================================================================================================

Inputs {.sidebar}
-------------------------------------------------------------------------

```{r}
filter_checkbox("type", "Choose cases or deaths", raw_weekly_long_shared, ~type)
filter_select("year_month", "Choose month of the year", raw_weekly_long_shared, ~year_month)
```

Column
-------------------------------------------------------------------------

### Weekly positive cases and deaths

```{r}
raw_weekly_long_shared %>%
  plot_ly(x = ~week, y = ~value, type = "bar", split = ~country, hovertext = ~sub_region)
```
